---
title: "Section 7 Overview"
output: 
  html_document:
    css: custom.css
    df_print: kable
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    runtime: shiny
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(cache=TRUE)

library(AdminLTE)
# library(bsplus)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(shiny)
library(shinydashboard)

source("micro/topline.R")

# dat <- readRDS("FWS_s7_03May2016.rds")
# dat_form <- filter(dat, formal_consult == "Yes")
all_cons <- 90950
form_cons <- 7543
all_time <- "14 days"
form_time <- "63 days"
```

Section 7 of the U.S. Endangered Species Act (ESA) is often considered the most
important section of the law. Any federal
agency whose actions may affect an ESA-listed species are required to consult
with the U.S. Fish and Wildlife Service (FWS) and/or the National Marine Fisheries
Service (NMFS) to ensure the action does not jeopardize the species' existence
or adversely modify or destroy its critical habitat. A federal action could mean
a number of things, such as:

- issuing a permit to dredge or fill a wetland (a Clean Water Act 404 permit);
- funding a highway project; or
- carrying out an activity, such as prescribed burns on a National Forest.

The reach and strength of section 7 means it is the focus of many arguments about
the ESA. Despite decades of argument, no one had checked to see what
the data had to say about how the section has been implemented. In 2015, we 
published the first complete analysis of section 7 consultations done by FWS 
in the ESA's 42-year history 
([Malcom and Li, 2015](http://www.pnas.org/content/112/52/15844.abstract)).
That analysis showed that common perceptions of how the section is implemented 
are often wrong.

This web application provides access to the entire dataset analyzed by Malcom
and Li, plus data updates provided by FWS since the publication."

# Data overview

## Count and duration

To get a scale of FWS's consultation program, considert the number of 
consultations - total and formal only - performed by FWS since January, 2015:

```{r topline_1, echo=FALSE, cache=FALSE}
# cons <- table(dat$formal_consult)

fluidPage(
  tags$head(tags$style(AdminLTE())),
  fluidRow(br()),
  fluidRow(
    column(6,
      renderValueBox(
        valueBox(
          subtitle = "# consultations",
          value = all_cons,
          color = "navy",
          icon = NULL,
          width = NULL
        )
      )
    ),
    column(6,
      renderValueBox(
        valueBox(
          subtitle = "# formal consultations",
          value = form_cons,
          color = "orange",
          icon = NULL,
          width = NULL
        )
      )
    )
  )
)
```

Now consider the duration of consultation - in terms of the time FWS performs 
the consultation - for these `r all_cons` consultations:

```{r topline_2, cache=FALSE, echo=FALSE}
# all_time <- paste(
#   median(dat$elapsed, na.rm = TRUE),
#   "days"
# )
# 
# form_time <- paste(
#   median(dplyr::filter(dat, formal_consult == "Yes")$elapsed, na.rm = TRUE),
#   "days"
# )

fluidPage(
  # tags$head( tags$style(AdminLTE()) ),
  fluidRow(br()),
  fluidRow(
    column(6,
      valueBox(
        subtitle = "Consultation duration (median)",
        value = all_time,
        color = "navy",
        icon = NULL,
        width = NULL
      )
    ),
    column(6,
      valueBox(
        subtitle = "Formal consultation duration",
        value = form_time,
        color = "orange",
        icon = NULL,
        width = NULL
      )
    )
  )
)
# topline(data = dat, select = FALSE)
```

## Through time

```{r thru_time_1, echo=FALSE, cache=FALSE}
# yr_all_dat <- aggregate(dat$ )
# thru_time(data = dat, select = FALSE)
```


