---
title: "Section 7 Overview"
output: 
  html_document:
    css: custom.css
    df_print: kable
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    runtime: shiny
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(cache=TRUE)

library(AdminLTE)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(shiny)
library(shinydashboard)

source("topline.R")
# tags$head( tags$style(AdminLTE()) )

dat <- readRDS("FWS_s7_03May2016.rds")
dat_form <- filter(dat, formal_consult == "Yes")
```

Section 7 of the U.S. Endangered Species Act (ESA) is often considered the most
important section of the law because of its reach and prohibitions. Any federal
agency whose actions may affect an ESA-listed species are required to consult
with the U.S. Fish and Wildlife Service (FWS) and/or the National Marine Fisheries
Service (NMFS) to ensure the action does not jeopardize the species' existence
or adversely modify or destroy its critical habitat. A federal action could mean
a number of things, such as:

- issuing a permit to dredge or fill a wetland (a Clean Water Act 404 permit);
- funding a highway project; or
- carrying out an activity, such as prescribed burns on a National Forest.

# Top-level Numbers

```{r test_tab, comment="This is a comment", echo=FALSE, cache=FALSE}
topline(dat)
```
